|

### 2021-03-15 documentation/paper.Rmd
Lower case project name and new documentation doi

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(BritPol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, Y, and Z. We would also like to extend a special thanks to all of the volunteers who have given their time to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("BritPol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(BritPol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

library(BritPol)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(tidybayes)
library(patchwork)
library(brms)
library(here)

@@

death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("BritPol"), ".rds")))

@@

cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("BritPol"), ".rds")))
cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("BritPol"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("BritPol"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))

@@

In this paper, we introduce PollBasePro: the most comprehensive time series of British voting intention data assembled to date. The dataset contains `r format(nrow(BritPol::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. Furthermore, our data are well validated and follow the course of British political history. We therefore expect PollBasePro to become a valuable resource for students of British politics in the years to come.

It is important to stress that PollBasePro is a *living dataset*. As a result, we expect to incorporate new estimates into the data as time goes by. Users should, therefore, endeavour to use the most recent data in any of their analyses. It is also important to stress that---like any project of this nature---our data pipeline might contain minor errors or inefficiencies. To guard against this, we have hosted all of our materials online for others to inspect. If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's [GitHub repository](https://github.com/jackobailey/BritPol/issues) or to [contact the authors directly](mailto:jack.bailey@manchester.ac.uk).

>>>>

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, Y, and Z. We would also like to extend a special thanks to all of the volunteers who have given their time to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("britpol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
linkcolor: black
urlcolor: violet
citecolor: black
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

library(britpol)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(tidybayes)
library(patchwork)
library(brms)
library(here)

@@

death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("britpol"), ".rds")))

@@

cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("britpol"), ".rds")))
cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("britpol"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("britpol"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("britpol"), ".rds")))

@@

In this paper, we introduce PollBasePro: the most comprehensive time series of British voting intention data assembled to date. The dataset contains `r format(nrow(britpol::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. Furthermore, our data are well validated and follow the course of British political history. We therefore expect PollBasePro to become a valuable resource for students of British politics in the years to come.

It is important to stress that PollBasePro is a *living dataset*. As a result, we expect to incorporate new estimates into the data as time goes by. Users should, therefore, endeavour to use the most recent data in any of their analyses. It is also important to stress that---like any project of this nature---our data pipeline might contain minor errors or inefficiencies. To guard against this, we have hosted all of our materials online for others to inspect. If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's [GitHub repository](https://github.com/jackobailey/britpol/issues) or to [contact the authors directly](mailto:jack.bailey@manchester.ac.uk).

### 2021-03-15 documentation/readme.Rmd
Lower case project name and new documentation doi

library(BritPol)
library(tidyverse)
library(lubridate)
library(here)

@@

# BritPol

BritPol is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. A user guide and codebook is available for `pollbasepro` [here](https://github.com/jackobailey/BritPol/blob/master/download/userguide.pdf) and an accompanying paper is available [here](https://github.com/jackobailey/BritPol/blob/master/download/paper.pdf).

To install the latest version of BritPol, run the following code in `R`:

``` r
devtools::install_github("jackobailey/BritPol")
```

We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users. These files include all necessary value and variable labels and should work seamlessly with both software packages. [Click here to download them](https://github.com/jackobailey/BritPol/tree/master/download).

@@

<center><img src="https://raw.githubusercontent.com/jackobailey/BritPol/master/documentation/_assets/timeplot_gh.png"></center>

@@

Both `pollbase` and `pollbasepro` are living datasets. As such, users should try to use only the most recent version of the data when conducting their analyses. Like any project of this size, some minor mistakes might have crept into the data processing pipeline. If you think that you have found an error in the code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/BritPol/issues).

Your may use any BritPol code for your own purposes, but you must do so *with attribution*. That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you used BritPol to produce your work. The citations for each item in BritPol are as follows:

### BritPol

- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) BritPol v`r packageVersion("BritPol")`: User Guide and Data Codebook. Retrieved from doi.

@@

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("BritPol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from https://doi.org/10.7910/DVN/3POIQW.

>>>>

library(britpol)
library(tidyverse)
library(lubridate)
library(here)

@@

# britpol

`britpol` is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. A user guide and codebook is available for `pollbasepro` [here](https://github.com/jackobailey/britpol/blob/master/download/userguide.pdf) and an accompanying paper is available [here](https://github.com/jackobailey/britpol/blob/master/download/paper.pdf).

To install the latest version of `britpol`, run the following code in `R`:

``` r
devtools::install_github("jackobailey/britpol")
```

We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users. These files include all necessary value and variable labels and should work seamlessly with both software packages. [Click here to download them](https://github.com/jackobailey/britpol/tree/master/download).

@@

<center><img src="https://raw.githubusercontent.com/jackobailey/britpol/master/documentation/_assets/timeplot_gh.png"></center>

@@

Both `pollbase` and `pollbasepro` are living datasets. As such, users should try to use only the most recent version of the data when conducting their analyses. Like any project of this size, some minor mistakes might have crept into the data processing pipeline. If you think that you have found an error in the code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/britpol/issues).

Your may use the `britpol` codebase for your own purposes, but you must do so *with attribution*. That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you used britpol to produce your work. The citations for each item in `britpol` are as follows:

### britpol

- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) britpol v`r packageVersion("britpol")`: User Guide and Data Codebook. Retrieved from https://doi.org/10.17605/OSF.IO/2M9GB.

@@

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("britpol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from https://doi.org/10.7910/DVN/3POIQW.

### 2021-03-15 documentation/userguide.Rmd
Lower case project name and new documentation doi

---
title: |
  | BritPol v`r packageVersion("BritPol")` (Beta)
  | User Guide and Data Codebook
date: |
  | This version: `r stringr::str_remove(format(Sys.time(), "%d %B %Y"), "^0")`
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/cb-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

library(BritPol)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(brms)
library(here)

@@

cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("BritPol"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("BritPol"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))

@@

# About BritPol

BritPol is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's [-@pack2021] dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

Both `pollbase` and `pollbasepro` are *living datasets*. Thus, users should endeavour to use only the most recent version of the data when conducting their analyses. This will become more important in the future, as we intend to add new polls and estimates over time. Likewise, we cannot rule out that minor mistakes might have crept into our data processing pipeline. To guard against this, we have made all of our materials available for others to inspect. If you find an error in the code or wish to make a recommendation for a future update, we invite you to raise an issue on the BritPol GitHub repository.

@@

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("BritPol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from https://doi.org/10.7910/DVN/3POIQW.

- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) BritPol v`r packageVersion("BritPol")`: User Guide and Data Codebook. Retrieved from doi.

@@

# Using BritPol

Getting started with BritPol in `R` is simple. It requires only three short steps: first, to install the package; second, to load the package; and, third, to load the data. Once you have taken these three steps, you can then begin analysing the data. Note that BritPol is not yet available on CRAN, the service that hosts most `R` packages. As such, it is not yet possible to install BritPol with `R`'s standard `install.packages()` function. Instead, we must install it directly from its GitHub repository. Thankfully this is straightforward and requires only that you run the following code in your `R` console:

```{r install-pbp, eval = FALSE}
# 1. Install the BritPol package from GitHub
devtools::install_github("jackobailey/BritPol")

# 2. Load the BritPol package in R
library(BritPol)

@@

Though BritPol is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too. To make this as easy as possible, we have made both the `pollbase` and `pollbasepro` datasets available as .dta and .sav files. These include all necessary value and variable labels and should work seamlessly with both software packages. You can download the latest version of the data by clicking the links below:

- ``r paste0("pollbase_", packageVersion("BritPol"), ".dta")``
- ``r paste0("pollbasepro_", packageVersion("BritPol"), ".dta")``
- ``r paste0("pollbase_", packageVersion("BritPol"), ".sav")``
- ``r paste0("pollbasepro_", packageVersion("BritPol"), ".sav")``

@@

We recognise that some users will find understanding our modelling decisions more simple if they were able to see our code^[Note that we estimate all of our models using `R` `r str_remove(R.Version()$version.string, "^R*.")` and either version `r packageVersion("brms")` of the `brms` package [@burkner2017] or version `r cmdstanr::cmdstan_version()` of `cmdstan`, an interface to the Stan probabilistic programming language [@carpenter2017]]. This transparency also has other benefits: it allows our users to identify mistakes in our code. After all---and like any project of this nature---our data pipeline likely contains minor errors or inefficiencies that could affect the estimates that we obtain. To guard against this, and provide our users with a more in-depth look at our modelling process, we have hosted our entire data pipeline online for others to inspect. If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's GitHub repository or to contact the authors directly.

@@

For the sake of openness and transparency, we provide a change log that lists all updates and changes made to BritPol over time. If you think that you have found a problem with either the data, code, or documentation, please raise an issue on the project's GitHub repository.

>>>>

---
title: |
  | britpol v`r packageVersion("britpol")` (Beta)
  | User Guide and Data Codebook
date: |
  | This version: `r stringr::str_remove(format(Sys.time(), "%d %B %Y"), "^0")`
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
linkcolor: black
urlcolor: violet
citecolor: black
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/cb-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

library(britpol)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(brms)
library(here)

@@

cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("britpol"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("britpol"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("britpol"), ".rds")))

@@

# About britpol

`britpol` is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's [-@pack2021] dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

Both `pollbase` and `pollbasepro` are *living datasets*. Thus, users should endeavour to use only the most recent version of the data when conducting their analyses. This will become more important in the future, as we intend to add new polls and estimates over time. Likewise, we cannot rule out that minor mistakes might have crept into our data processing pipeline. To guard against this, we have made all of our materials available for others to inspect. If you find an error in the code or wish to make a recommendation for a future update, we invite you to [raise an issue on the `britpol` GitHub repository](https://github.com/jackobailey/britpol/issues).

@@

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("britpol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from https://doi.org/10.7910/DVN/3POIQW.

- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) britpol v`r packageVersion("britpol")`: User Guide and Data Codebook. Retrieved from https://doi.org/10.17605/OSF.IO/2M9GB.

@@

# Using britpol

Getting started with `britpol` in `R` is simple. It requires only three short steps: first, to install the package; second, to load the package; and, third, to load the data. Once you have taken these three steps, you can then begin analysing the data. Note that `britpol` is not yet available on CRAN, the service that hosts most `R` packages. As such, it is not yet possible to install `britpol` with `R`'s standard `install.packages()` function. Instead, we must install it directly from its [GitHub repository](https://github.com/jackobailey/britpol). Thankfully this is straightforward and requires only that you run the following code in your `R` console:

```{r install-pbp, eval = FALSE}
# 1. Install the britpol package from GitHub
devtools::install_github("jackobailey/britpol")

# 2. Load the britpol package in R
library(britpol)

@@

Though `britpol` is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too. To make this as easy as possible, we have made both the `pollbase` and `pollbasepro` datasets available as .dta and .sav files. These include all necessary value and variable labels and should work seamlessly with both software packages. You can download the latest version of the data by clicking the links below:

- ``r paste0("pollbase_", packageVersion("britpol"), ".dta")``
- ``r paste0("pollbasepro_", packageVersion("britpol"), ".dta")``
- ``r paste0("pollbase_", packageVersion("britpol"), ".sav")``
- ``r paste0("pollbasepro_", packageVersion("britpol"), ".sav")``

@@

We recognise that some users will find understanding our modelling decisions more simple if they were able to see our code^[Note that we estimate all of our models using `R` `r str_remove(R.Version()$version.string, "^R*.")` and either version `r packageVersion("brms")` of the `brms` package [@burkner2017] or version `r cmdstanr::cmdstan_version()` of `cmdstan`, an interface to the Stan probabilistic programming language [@carpenter2017]]. This transparency also has other benefits: it allows our users to identify mistakes in our code. After all---and like any project of this nature---our data pipeline likely contains minor errors or inefficiencies that could affect the estimates that we obtain. To guard against this, and provide our users with a more in-depth look at our modelling process, we have hosted our entire data pipeline online for others to inspect. If our users find any errors in our code or wish to make recommendations for future updates, we invite them to [raise an issue on the project's GitHub repository](https://github.com/jackobailey/britpol/issues) or to [contact the authors directly](mailto:jack.bailey@manchester.ac.uk).

@@

For the sake of openness and transparency, we provide a change log that lists all updates and changes made to `britpol` over time. If you think that you have found a problem with either the data, code, or documentation, please [raise an issue on the project's GitHub repository](https://github.com/jackobailey/britpol/issues).
